GO

### 2020-03-28 analysis/12_GO.Rmd
?

```{r GO_DEGs}
GO_DEGs <- left_join(allGO, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>% 
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, 
         #contains("control_bldg"), 
         contains("bldg_lay"), contains("lay_inc.d3"),
         contains("inc.d3_inc.d9"), contains("inc.d9_inc.d17"), contains("inc.d17_hatch"),
         contains("hatch_n5"), contains("n5_n9")) %>%
  filter(GO %in% c("endocrineprocess", "lactation", 
                   "parentalbehavior", "matingbehavior", "reproduction",
                   "candidategenes", "cellcycleprocess")) %>% 
  map(~.x) %>%
  discard(~all(is.na(.x))) %>%
  map_df(~.x)
head(GO_DEGs)
```

@@

```{r bytissue}
hyp <- GO_DEGs %>% select(GO, starts_with("male_hyp"), starts_with("female_hyp"))
pit <- GO_DEGs %>% select(GO, starts_with("male_pit"), starts_with("female_pit"))
gon <- GO_DEGs %>% select(GO, starts_with("male_gon"), starts_with("emale_gon"))

kable(hyp)  
# top GO therms for hyp:
# endocrine process, regulation of hormone levels,
# signal release # hormone secretion, # system process
# hormone transport, cell-cell signaling

kable(pit)
# endocrine process, mating behavior, system process,
# reproductive behavior, mating, regulation of blood pressure
# signal release, regulation of hormone levels

kable(gon)  
# endocrine process, regulation of blood pressure
# blood circutation, circulatory system
```

## Candidate genes

```{r}
candidate_DEGs <- left_join(candidates, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>%
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control_bldg"), contains("bldg_lay"), contains("lay_inc.d3"),
         contains("inc.d3_inc.d9"), contains("inc.d9_inc.d17"), contains("inc.d17_hatch"),
         contains("hatch_n5"), contains("n5_n9"))
candidate_DEGs <- as.data.frame(candidate_DEGs)

row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
kable(candidate_DEGs) 
```

```{r write}
write.csv(GO_DEGs, "../results/12_GO_DEGs.csv")
write.csv(hyp, "../results/12_GO_DEGs_hyp.csv")
write.csv(pit, "../results/12_GO_DEGs_pit.csv")
write.csv(gon, "../results/12_GO_DEGs_gon.csv")
```

>>>>

```{r GO_DEGs}
GO_DEGs <- left_join(allGO, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>% 
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, 
         #contains("control_bldg"), 
         contains("bldg_lay"), contains("lay_inc.d3"),
         contains("inc.d3_inc.d9"), contains("inc.d9_inc.d17"), contains("inc.d17_hatch"),
         contains("hatch_n5"), contains("n5_n9")) %>%
  filter(GO %in% c("endocrineprocess", "lactation", 
                   "parentalbehavior", "matingbehavior", "reproduction",
                   "candidategenes", "cellcycleprocess")) %>% 
  map(~.x) %>%
  discard(~all(is.na(.x))) %>%
  map_df(~.x)
#head(GO_DEGs)
```

@@

```{r bytissue}
fhyp <- GO_DEGs %>% select(GO, starts_with("female_hyp"))
mhyp <- GO_DEGs %>% select(GO, starts_with("male_hyp"))

fpit <- GO_DEGs %>% select(GO, starts_with("female_pit"))
mpit <- GO_DEGs %>% select(GO, starts_with("male_pit"))

fgon <- GO_DEGs %>% select(GO, starts_with("female_gon"))
mgon <- GO_DEGs %>% select(GO, starts_with("male_gon"))

kable(fhyp) 
kable(mhyp)

kable(fpit)
kable(mpit)

kable(fgon) 
kable(mgon)

```{r write}
write.csv(GO_DEGs, "../results/12_GO_DEGs.csv")
#write.csv(hyp, "../results/12_GO_DEGs_hyp.csv")
#write.csv(pit, "../results/12_GO_DEGs_pit.csv")
#write.csv(gon, "../results/12_GO_DEGs_gon.csv")
```
